\documentclass{scrreprt} % comment this out when done editing
% \documentclass{standalone}
% \usepackage{standalone}
\usepackage{chez}

\begin{document}

\section{Unit 02}

Knowing the different types of unemployment and when they occur is an integral
part of the AP Macroeconomics syllabus. Thus, understanding the characteristics
of the different types of unemployment is necessary. Unemployment comes in three
forms: cyclical, structural, and frictional.

\begin{enumerate}
	\item  Cyclical unemployment is the result of a downturn in the business cycle.
This type of unemployment is temporary and only occurs when there is a contraction in the economy.
An example of cyclical unemployment is someone who is laid off because a company isn't selling enough due to a recession and can't afford to pay them.

	\item Structural Unemployment - Structural unemployment occurs when the skills of workers do not meet the skills demanded of such workers by employers.
This type of unemployment often occurs as a result of technological change, resulting in workers’ skills becoming obsolete.
An example of structural unemployment is a typewriter repairman. While they may have been necessary in the 1950s, nobody has a typewriter anymore and thus the typewriter repairman is out of a job.
	\item Frictional Unemployment
\begin{itemize}
	\item Workers are between jobs
	\item Workers have just entered the workforce and are yet to find a job.
	\item An example of someone who is frictionally unemployed is someone who quits a job and is looking for a new one.
	\item Natural Rate of Unemployment
	\item Finally, the concept of the natural rate of unemployment is the key to
	understanding unemployment in the
	macroeconomy
\end{itemize}
\end{enumerate}

\begin{remark}

The natural rate of unemployment is defined as the combination of structural and frictional unemployment present in an efficient expanding economy in macro equilibrium.
Basically, it means that there is no cyclical unemployment, not no unemployment at all. There will ALWAYS be some frictional and structural unemployment, as there will always be people in between jobs or without necessary skills for a job
Why is this? Well, it makes sense, you can never employ EVERY member of a labor force because some people might quit their job and be frictionally unemployed or someone might not be able to get a job with their skills. In fact, a 0\% unemployment rate would be a red flag to any economist.
In the United States, this rate is between 4-6\%, which is why aiming for a 0\% rate of unemployment is dangerous to the health of our economy.
For the AP Exam, typically, unemployment from 0\% - 3 or 4\% implies an inflationary gap, 4-6\% is full employment, 7\%+ is a recessionary gap (they will make it glaringly obvious, something like either 2\% or 10\%, or they might flat out say "recession")
At 0\% unemployment, inflation would be high, rising prices

\end{remark}

\begin{definition}
	Unemployment means that you are currently looking for a job, but you can't find one.
\end{definition}

\begin{definition}
	Discouraged workers are workers who are not employed because they are not
	qualified or because they are not in a position to be employed. Aka,
	they give up.
\end{definition}

\begin{definition}
	Our full employment is the combination of employed and unemployed workers.
\end{definition}

\begin{remark}
	Retired people are not considered unemployed because they are not looking for a job.
\end{remark}

People who are not in the labor force include:

\begin{itemize}
	\item Military
	\item Children
	\item Jail
	\item Stay-at-home people
	\item Full-time students
\end{itemize}

\begin{remark}
	The goal is to not be fully employed, but rather have 3-5 percent of the population
	unemployed and we want to minimize cyclical unemployment.
\end{remark}

\subsection{September 21, 2021}

\begin{definition}
	Labor force participation rate = Labor force / Population age 16 or older times 100

	Unemployment rate = Unemployment / Full employment times 100
\end{definition}

\begin{example}
	Given the following circumstnace, how many are in the labor force?

	\begin{itemize}
		\item 1000 people > 16
		\item 475 civilians employed
		\item 200 full time students
		\item 100 stay-at-home parents
		\item 25 active job seekers
	\end{itemize}

	\begin{align*}
		475 + 25 &= 500 \quad \text{people are in the labor force} \\
		\frac{475}{500} &= 95 \text{\% unemployment} \\
		\frac{25}{500} &= 5 \text{\% unemployment} \\
		\frac{500}{1000} &= 50 \text{\% labor force employment}
	\end{align*}

	\begin{align*}
		\sum W &= 15,000 + 8,000 + 2,000 = 25,000 \text{people are in the labor force} \\
		\frac{2000}{25000} &= 8 \text{\% unemployment} \\
		\frac{25000}{32000} &= 78.125 \text{\% labor force participation} \\
		\frac{3000}{25000} &= 12 \text{\% discouraged rate}
	\end{align*}
\end{example}

\end{document}